Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-12-15 02_Paper/paper.tex
Author Contributions

We compared a total of three different classifier architectures on the data,
a Support Vector Machine (SVM), a Multilayer Perceptron (MLP) and a Decision Tree
structure. In this case, we chose to train all three models using exemplary 
default hyperparameters, which we found to work.
\footnote{To allow exact reproduction of our results source code
 is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}

@@

Pérez M. and Wolter performed writing - original draft, conceptualization, review, and editing; investigation; software and data curation.
Schmallenbach performed writing - review \& editing.
Wagner, Heinbach, Steinberg, Garcke, and Steffes-lai performed writing - review.
Burggräf performed supervision of work.

>>>>

We compared a total of three different classifier architectures on the data,
a Support Vector Machine (SVM), a Multilayer Perceptron (MLP) and a Decision Tree
structure. In this case, we chose to train all three models using exemplary 
default hyperparameters, which we found to work well.
\footnote{To allow exact reproduction of our results source code
 is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}

@@

Pérez M. and Wolter performed writing - original draft, conceptualization, review, and editing; investigation; software and data curation.
Schmallenbach performed writing - review \& editing.
Burggräf, Wagner, Heinbach, Steinberg performed writing - conceptualization, review.
Garcke, and Steffes-lai performed writing - review.
% Burggräf performed supervision of work.
